\documentclass[letterpaper,10pt]{article}

% -------------------- Packages --------------------
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{tabularx}

% -------------------- Page Setup --------------------
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.45in}
\addtolength{\textwidth}{0.90in}
\addtolength{\topmargin}{-0.55in}
\addtolength{\textheight}{1.10in}

\raggedright
\setlength{\tabcolsep}{0in}

% -------------------- Section Formatting --------------------
\titleformat{\section}
  {\vspace{-2pt}\scshape\raggedright\large}
  {}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% -------------------- Custom Commands --------------------
\newcommand{\resumebullet}{\raisebox{0.2ex}{\tiny$\bullet$}}

\newcommand{\resumeItem}[1]{
  \item \small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
  \begin{tabularx}{\textwidth}{X r}
    \textbf{#1} & \textbf{#2} \\
    \textit{\small #3} & \textit{\small #4} \\
  \end{tabularx}\vspace{-6pt}
}

\newcommand{\resumeSubheadingOneLine}[2]{
  \vspace{-1pt}\item
  \begin{tabularx}{\textwidth}{X r}
    \textbf{#1} & \textbf{#2} \\
  \end{tabularx}\vspace{-6pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*, itemsep=2pt, topsep=2pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*, label={}, itemsep=3pt, topsep=2pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-6pt}}

% Tighten list bullets
\setlist[itemize]{noitemsep, topsep=2pt}

% -------------------- Document --------------------
\begin{document}

% -------------------- Header --------------------
\begin{tabularx}{\textwidth}{X r}
  {\LARGE \textbf{Duncan Clark}} & \href{mailto:clark.a.duncan@gmail.com}{clark.a.duncan@gmail.com} \\
  \textbf{Portfolio Analytics / Decision Science} & (310) 254-6345 \\
  \href{http://duncan-clark.github.io}{duncan-clark.github.io} & \\
\end{tabularx}
\vspace{-6pt}

% -------------------- Summary --------------------
\section{Summary}
\small{
Decision-focused data scientist with experience in Big Tech and healthcare analytics, specializing in causal inference, risk/impact measurement, and scalable data/ML systems. Proven track record building metrics and models that change investment decisions and engineering priorities (e.g., quantified large operational savings; delivered privacy and compliance analytics at scale). Strong foundations in finance and liability modeling from actuarial work; PhD-trained statistician with expertise in uncertainty quantification and structured dependence (networks).
}
\vspace{-2pt}

% -------------------- Core Skills --------------------
\section{Core Skills}
\small{
\textbf{Decision \& Measurement:} causal inference, A/B impact estimation, sensitivity analysis, KPI design, uncertainty quantification, scenario thinking \\
\textbf{Modeling:} survival analysis, supervised learning, embeddings, differential privacy (DP) measurement and accounting \\
\textbf{Data \& Systems:} Python, R, SQL, AWS, production data pipelines, model serving, data validation/auditing \\
\textbf{Domains:} privacy analytics \& governance, healthcare/HR analytics, actuarial liability modeling, portfolio-style risk reasoning
}
\vspace{-4pt}

% -------------------- Experience --------------------
\section{Industry Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Meta Platforms, Inc.}{New York City, NY}
    {Research Data Scientist}{Aug 2022 -- Aug 2023}
    \resumeItemListStart
      \resumeItem{\textbf{Built decision-driving measurement for privacy programs} by partnering with engineers and privacy experts to quantify the impact of data minimization and de-identification efforts across large-scale data systems.}
      \resumeItem{\textbf{Developed privacy cost metrics} to estimate engineering effort required for privacy compliance; created frameworks to prioritize high-ROI interventions and guide strategic investment.}
      \resumeItem{\textbf{Designed a graph-based view of data flows} to reason about privacy footprint and compliance cost; used causal methods to estimate effects and support leadership decisions.}
      \resumeItem{\textbf{Differential privacy expertise:} advised teams on DP aggregation risks in SQL workloads; identified common leak patterns and improved safeguards.}
      \resumeItem{\textbf{Implemented DP training components} including a differential privacy accountant for open-source private training (Opacus), enabling more rigorous privacy guarantees in model training workflows.}
    \resumeItemListEnd

  \resumeSubheading
    {Meta Platforms, Inc.}{New York City, NY}
    {Research Data Scientist Intern}{Jun 2021 -- Sept 2021}
    \resumeItemListStart
      \resumeItem{\textbf{Improved evaluation validity} by advising on sampling methods for unbiased performance estimation on semantic type classification tasks.}
      \resumeItem{\textbf{Reduced training time while improving performance} by proposing a simpler alternative model to an in-house deep learning approach.}
    \resumeItemListEnd

  \resumeSubheading
    {Meta Platforms, Inc.}{Remote / Menlo Park, CA}
    {Infrastructure Data Scientist Intern}{Jun 2020 -- Sept 2020}
    \resumeItemListStart
      \resumeItem{\textbf{Predicted production app performance regressions} from beta testing signals; iterated on models under noisy, high-scale conditions.}
      \resumeItem{\textbf{Reduced false positives by \raisebox{0.2ex}{\small\textasciitilde}90\%} through feature refinement and workflow improvements, improving engineer trust and actionability.}
    \resumeItemListEnd

  \resumeSubheading
    {Atalan Tech}{Remote (USA)}
    {Data Scientist \& Engineer}{Jun 2023 -- May 2024}
    \resumeItemListStart
      \resumeItem{\textbf{Led end-to-end modeling for clinician burnout prediction} by reframing the problem as survival analysis and improving performance versus prior baselines.}
      \resumeItem{\textbf{Built granular procedure-code embeddings} (deep learning) to capture fine clinical signals, enabling stronger predictive performance with heterogeneous client data.}
      \resumeItem{\textbf{Designed scalable AWS-backed systems} for serving ML models and enforcing data validity across multiple enterprise clients with heterogeneous schemas.}
      \resumeItem{\textbf{Established auditable ML and data controls} (validation, monitoring, reproducibility practices) and coached the data science team on robust delivery.}
      \resumeItem{\textbf{Partnered with economics researchers} on statistical methods and analyses contributing to conference-facing outputs.}
    \resumeItemListEnd

  \resumeSubheading
    {Xafinity Consulting}{Reading, United Kingdom}
    {Actuarial Analyst}{Sep 2015 -- Sep 2017}
    \resumeItemListStart
      \resumeItem{\textbf{Modeled defined benefit pension liabilities} (valuations, transfer values, accounting disclosures, assumption setting) with high attention to governance and risk drivers.}
      \resumeItem{\textbf{Selected for specialist pension insurance team} supporting large bespoke schemes; delivered rapid turnaround analyses for multiple deals exceeding \pounds 1B.}
      \resumeItem{\textbf{Finance foundations:} Institute and Faculty of Actuaries exams passed (CT1--CT8), \textasciitilde60\% completed.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

% -------------------- Education --------------------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {University of California, Los Angeles (UCLA)}{Los Angeles, CA}
    {PhD, Statistics \ \ (\small GPA: 3.89/4.00)}{Sep 2017 -- Jun 2022}
  \resumeSubheading
    {University College London (UCL)}{London, UK}
    {MSci Mathematics, First Class Honors}{Sep 2011 -- Jun 2015}
\resumeSubHeadingListEnd

% -------------------- Selected Research (Optional, slim) --------------------
\section{Selected Research (Optional)}
\small{
\textbf{Network \& dependence modeling:} publications and preprints on statistical models for networks and spatiotemporal processes; invited talks at Penn State (2025) and UCSC (2025). \\
\textbf{Award:} UCLA Department of Statistics Outstanding PhD Dissertation Award (2022).
}
\vspace{-4pt}

% -------------------- Additional --------------------
\section{Additional}
\resumeSubHeadingListStart
  \resumeSubheadingOneLine{Programming}{Python, R, SQL, C++, AWS}
  \resumeSubheadingOneLine{Service}{Reviewer: Journal of Complex Networks}
\resumeSubHeadingListEnd

\end{document}
